prolfqua - An R-package for Proteomics Differential Expression Analysis.

### 2022-05-06 inst/MyArticle/paper.Rmd
cosmetics in referencing R packages

The r-package proDA and prolfqua model the missing data directly, while MSstats imputes the data using an accelerated failure model. Despite imputation, MSstats do not estimate group differences for more proteins and do not achieve a higher pAUC score than prolfqua. Furthermore, \@ref(fig:FDRfdp) Panel C shows that when using MSstats the proportion of false discoveries might be very high even when filtering for a low FDR.

>>>>

The R-package `r BiocStyle::Biocpkg("proDA")` and `r BiocStyle::Biocpkg("prolfqua")` model the missing data directly, while MSstats imputes the data using an accelerated failure model. Despite imputation, MSstats do not estimate group differences for more proteins and do not achieve a higher pAUC score than prolfqua. Furthermore, \@ref(fig:FDRfdp) Panel C shows that when using MSstats the proportion of false discoveries might be very high even when filtering for a low FDR.
